As-you-go" instead of "after-the-fact": A network approach to scholarly communication and evaluation

### 2018-03-30 docs/manuscript.Rmd
Revise last use case

  Individual researchers can use networks to better understand their research outputs and plan new research efforts. For example, simply visualizing a network of outputs could already prove a useful tool for researchers to view relationships between their outputs from a different, more coherent perspective. Researchers looking for new research opportunities could also use network analysis to identify their strengths, by comparing whether specific sets of outputs are more central than others in a larger network. For example, a researcher who writes software for their research might find that their software is more central in a larger network than their findings, which could indicate a fruitful specialization.

  One scenario where network evaluation tools could be valuable for individual researchers is in order to optimize resource allocation. A researcher might want to revisit previous work and conduct a large replication, but only has funds for one replication. Imagine a researcher who wants to identify an effect previously studied that has been central to their new research efforts. Identifying which effect to replicate is intended by this researcher as a safeguard mechanism to prevent further investment in new studies, if a fundamental finding proves to not be replicable.

  In this scenario, the researcher aims to identify the most central finding in a network. The researcher has conducted many studies throughout their career and does not want to identify the most central finding in the entire network of outputs over the years, but only of the most recent domain they've been working in. As such, the researcher takes the latest output and traces all the preceding outputs automatically, to create a subset of the full network and to incorporate potential work not done by themselves.

@@

  Centrality can be a useful measure to identify which finding to replicate, but would fail to take into account what replications have already been conducted. When taking the most recent output and looking at its parent(s), grandparent(s), etc., this only looks at the lineage of the finding. However, the children of all these parents are not taken into account in such a trace. As such, the researcher in our scenario might identify an important piece of research to replicate, but neglect that it has already been replicated. Without further inspection of the network for already available replications, resource allocation might be suboptimal after all.

>>>>

  Individual researchers could use networks to better understand their research outputs and plan new research efforts. For example, simply visualizing a network of outputs could prove a useful tool for researchers to view relationships between their outputs from a different perspective. Researchers looking for new research opportunities could also use network analysis to identify their strengths, by comparing whether specific sets of outputs are more central than others in a larger network. For example, a researcher who writes software for their research might find that their software is more central in a larger network than their theoretical work, which could indicate a fruitful specialization.

  One scenario where network evaluation tools could be valuable for individual researchers is resource allocation needs to be optimized. A researcher might want to revisit previous work and conduct a replication, but only has funds for one such replication. Imagine a researcher wants to identify an effect that they previously studied and which has been central to their new research efforts. Identifying which effect to replicate is intended by this researcher as a safeguard mechanism to prevent further investment in new studies, if a fundamental finding proves to not be replicable.

  In this resource allocation scenario, the researcher aims to identify the most central finding in a network. The researcher has conducted many studies throughout their career and does not want to identify the most central finding in the entire network of outputs over the years, but only of the most recent domain they've been working in. As such, the researcher takes the latest output and traces all the preceding outputs automatically to five generations, to create a subset of the full network and to incorporate potential work not done by themselves.

@@

  Katz centrality can be a useful measure to identify which finding to replicate in a multi-generational network, but would fail to take into account what replications have already been conducted. When taking the most recent output and looking at its parent(s), grandparent(s), etc., this only looks at the lineage of the finding. However, the children of all these parents are not taken into account in such a trace. As such, the researcher in our scenario might identify an important piece of research to replicate, but neglect that it has already been replicated. Without further inspection of the network for already available replications, resource allocation might be suboptimal after all.
